### 2016-09-30 projects_that_depend_on_sympy.tex
"module" -> "package" (based on what we said in the rebuttal)
The other ones say "Python package" so this one should too

\href{https://github.com/brombo/galgebra}{\textbf{galgebra}} &
  A module for geometric algebra (previously \texttt{sympy.galgebra})~\cite{galgebra}. \\

>>>>

\href{https://github.com/brombo/galgebra}{\textbf{galgebra}} &
  A Python package for geometric algebra (previously \texttt{sympy.galgebra})~\cite{galgebra}. \\
